---
title: "Disha_Project"
output:
  html_document:
    fig_height: 4
    highlight: pygments
    theme: spacelab
  pdf_document: default
  word_document: default
---

## Setup
```{r}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir= 'C:/Users/Admin/Desktop/R project/')
knitr::opts_chunk$set(error = FALSE)
```

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(tables)
```

### Load data

```{r load-data}
load("brfss2013.Rdata")
```

* * *

## Part 1: Data
In this case, the BRFSS Survey takes place every year from all 50 states and the District of Columbia, Puerto Rico, and Guam and collect survey data over a limited point- in-time (usually one to three months) from American Samoa, Federated States of Micronesia, and Palau. This makes the data generalized. 
The survey is conducted through both landline telephone and cellular telephone-based. In conducting the BRFSS landline telephone survey, interviewers collect data from a randomly selected adult in a household. In conducting the cellular telephone version of the BRFSS questionnaire, interviewers collect data from an adult who participates by using a cellular telephone and resides in a private residence or college housing. This makes the data collection random.

* * *

## Part 2: Research questions

**Research quesion 1:**
Does the number of responses for general health of household depend on the last time they had a checkup?

**Research quesion 2:**
People with children at home and how often they smoke and drink.

**Research quesion 3:**
A person being detected with cholestrol as compared to his exercises and food?

* * *

## Part 3: Exploratory data analysis

**Research quesion 1:**
Does the number of responses for general health of household depend on the last time they had a checkup?

The answer to question seems to be a no. As the amout of people who answer either of the options seem to fairly equal even though the last time they had a check up was 2 or 5 years ago or even never. This tells us how unreliable the data is until further investigation.

```{r}
ggplot(data=brfss2013)+geom_bar(aes(x=checkup1,fill=genhlth),position="fill")
```


**Research quesion 2:**
People with children at home and how often they smoke and drink.

The table shows the number of people who smoke(3 categories) and drink(0 or more than 100 drinks) with number of children in household. This data can help child services to identify children who might be affected by the adults and can be a victim of domestic violence.
```{r}
alccount=ifelse(brfss2013$alcday5==0,0,100)
mytable <- xtabs(~ children + alccount + smokday2, data=brfss2013)
ftable(mytable)
```



**Research quesion 3:**
A person being detected with cholestrol as compared to his exercises and food?

Here the people who have green vegetables and exercise also tend to have high cholestrol. The food habit and exercise routine doesnt have an affect any result of cholestrol as the data is equally divided into both categories..

```{r}
greens=ifelse(brfss2013$fvgreen>100,"good","bad")
mytable <- xtabs(~ toldhi2 + greens + exerany2, data=brfss2013)
ftable(mytable)
```


